Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-16 paper/main.tex
modify section nesting
use new profile plots

@@

%###################################################################################################
\section{Application 1: Elastic deformations of \textit{E.Coli}}

@@

\begin{figure}[H]
    \centering
    \begin{minipage}{0.38\textwidth}
        \begin{tikzonimage}[width=\textwidth]
            {figures/amir-elastic-000032-wider.png}%
            \node at (0.01, 0.01+17pt)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
        \end{tikzonimage}%
    \end{minipage}%
    \begin{minipage}{0.62\textwidth}
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/fit-comparison.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/drag force.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{C}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/growth rate.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
        \end{tikzonimage}\\
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/rod rigidity.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/spring tension.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{F}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-full/damping.pdf}%
            \node at (0.15, 0.86)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{G}};
        \end{tikzonimage}%
    \end{minipage}
    \caption{
        \textbf{TODO rework caption}
        Subfigure (A) shows a snapshot of the experiments performed by \cite{Amir2014_2}.
        Division of the bacteria is inhibited and they are partially trapped within a mother machine
        such that a controlled flow can be exerted on them.
        (B) A comparison of the initial and bent state show good visual agreement of our prediction
        with the experimental data.
        Subfigures (C-G) show likelihood profiles for the individual parameters.
    }
    \label{fig:amir-bending-simulation}
\end{figure}

%###################################################################################################
\section{Application 2: \textit{E.Coli.} growing on Agar}
\label{section:application-2}
To show the usefulness of our previously developed methods
(see section~\ref{section:parameter-estimation}), we will use them to estimate the parameters of
individually growing \textit{E.Coli} using a sequence of microscopic images.
The data we use~\cite{https://doi.org/10.3203/iwf/k-129} (see
section~\ref{section:data-code-availability}) has been automatically segmented with the
omnipose~\cite{Cutler2022} algorithm to obtain the required cell masks.

@@

% --------------------------------------------------------------------------------------------------
\subsection{Individual Treatment}

@@

% --------------------------------------------------------------------------------------------------
\subsection{With Division}

>>>>

\section{Applications}

@@

%###################################################################################################
\subsection{Application 1: Elastic deformations of \textit{E.Coli}}

@@

\begin{figure}[H]
    \centering
    \begin{minipage}{0.38\textwidth}
        \begin{tikzonimage}[width=\textwidth]
            {figures/amir-elastic-000032-wider.png}%
            \node at (0.01, 0.01+17pt)[anchor=north west, rectangle, draw, white, minimum width=15pt, minimum height=15pt]{\textbf{A}};
        \end{tikzonimage}%
    \end{minipage}%
    \begin{minipage}{0.62\textwidth}
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles-reduced/fit-comparison.pdf}%
            \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles/drag_force.pdf}%
            \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{C}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles/growth_rate.pdf}%
            \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
        \end{tikzonimage}\\
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles/rod_rigidity.pdf}%
            \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles/damping_to_spring_tension_ratio.pdf}%
            \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{F}};
        \end{tikzonimage}%
        \begin{tikzonimage}[width=0.33\textwidth]
            {figures/crm_amir/profiles/damping-spring_tension.pdf}%
            \node at (0.13, 0.88)[anchor=north west, black, minimum width=15pt, minimum height=15pt]{\textbf{G}};
        \end{tikzonimage}%
    \end{minipage}
    \caption{
        \textbf{TODO rework caption}
        Subfigure (A) shows a snapshot of the experiments performed by \cite{Amir2014_2}.
        Division of the bacteria is inhibited and they are partially trapped within a mother machine
        such that a controlled flow can be exerted on them.
        (B) A comparison of the initial and bent state show good visual agreement of our prediction
        with the experimental data.
        Subfigures (C-G) show likelihood profiles for the individual parameters.
    }
    \label{fig:amir-bending-simulation}
\end{figure}

%###################################################################################################
\subsection{Application 2: \textit{E.Coli.} growing on Agar}
\label{section:application-2}
To show the usefulness of our previously developed methods
(see section~\ref{section:parameter-estimation}), we will use them to estimate the parameters of
individually growing \textit{E.Coli} using a sequence of microscopic images.
The data we use~\cite{https://doi.org/10.3203/iwf/k-129} (see
section~\ref{section:data-code-availability}) has been automatically segmented with the
omnipose~\cite{Cutler2022} algorithm to obtain the required cell masks.

@@

% --------------------------------------------------------------------------------------------------
\subsubsection{The role of Heterogeneity}

@@

% --------------------------------------------------------------------------------------------------
\subsubsection{With Division}
